\LARGE \bf Detection of design pattern : A systematic mapping study

### 2016-01-02 article/main.tex
[fix] typo

The screening phase was done with the help of a spreadsheet where a column was
created for each evaluator.
Each evaluator was intructed to rate each article he's been assigned with a number
from 1 to 5, where 5 corresponds to the acceptation of the article and numbers below
to the applicable rejection criteron as defined in the previous section.
To prevent the rejection of relevant article, raters were instructed to accept
any article susceptible of being relevant with the afterthought that it could be
rejected after a complete reading.

>>>>

The screening phase was done with the help of a spreadsheet where a column was
created for each evaluator.
Each evaluator was instructed to rate each article he's been assigned with a number
from 1 to 5, where 5 corresponds to the acceptation of the article and numbers below
to the applicable rejection criterion as defined in the previous section.
To prevent the rejection of relevant article, raters were instructed to accept
any article susceptible of being relevant with the afterthought that it could be
rejected after a complete reading.
